e9_altsAnalysis

### 2015-10-20 analysis/e11_analysis.Rmd
checking for compliance of training trials - appears we had 100% compliance on e11

Experiment e11 - Pragmatic Listener experiment with alternatives
```{r}

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")
# commentary on weird RMarkdown bug
# https://github.com/hadley/xml2/issues/34
```

@@

Holding off on exclusions (but exclusion code here)
---------------------------------------------------
```{r}
d <- d.raw %>% filter(scale != "training1")
# compliant <- d.raw %>% 
#   filter(grepl("training", scale)) %>%
#   group_by(workerid) %>%
#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
#               judgment[scale == "training1" & degree == "low"] < 3)
#   
# d <- d.raw %>% 
#   left_join(compliant) %>%
#   filter(grepl(pattern = "english", 
#                language, ignore.case = TRUE), 
#          domain != "training1", 
#          domain != "training2", 
#          compliant == TRUE)
```

@@

Let's remove training runs
```{r}
#d.raw = d.raw[c(-1, -2), ]       # remove first two rows
#d = d.raw %>% filter(scale != "training1")
```

Populate a new df
```{r}
density <- d %>%
  group_by(degree, scale) %>%
  mutate(n = n()) %>%
  group_by(degree, scale, stars) %>%
  summarise(prop = n() / n[1])
```

Plot our pragmatic listener judgments
```{r}
write.csv(density, "models/e11.csv", row.names=FALSE)
pdf("plots/e11.pdf", width = 8, height = 4)
qplot(stars, prop, facets = degree ~ scale, 
      geom="bar", stat = "identity",
      binwidth = 1, data=density)
dev.off()
```

```{r}
# prop.calc = function(scalar, degree, stars, df) {
#   total = sum(df[(df$scale == scalar) & (df$degree == degree), "cnt.judgment"])
#   prop = df[(df$scale == scalar) & (df$degree == degree) & (df$stars = stars), "cnt.judgment"]
#   return(prop / total)
# }
# scales = rep("some_all", 5)
# stars = seq(1:5)
# degree = rep("hi1", 5)
# cnt.judgment = c(0, 0, 0, 2, 28)
# 
# df = data.frame(scales, stars, degree, cnt.judgment)
# prop.calc("some_all", "hi1", 1, df)
# 
# ms$judgment.prop = ms$judgment
# # write to csv for model
# #write.csv(ms, "models/e10.csv", row.names=FALSE)

```

>>>>

Experiment e11 - Pragmatic Listener experiment with alternatives
```{r}
rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")
library(ggplot2)
# commentary on weird RMarkdown bug
# https://github.com/hadley/xml2/issues/34
```

@@

Holding off on exclusions (but exclusion code here)
---------------------------------------------------
```{r}
# Make sure people answered training trials correctly
compliant <- d.raw %>% 
   filter(grepl("training", scale)) %>%
   group_by(workerid) %>%
   summarise(compliant = stars[scale == "training1" & degree == "hi2"] > 3 & 
               stars[scale == "training1" & degree == "low1"] < 3)

d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         scale != "training1", 
         scale != "training2", 
         compliant == TRUE)

# remove training runs
d <- d.raw %>% filter(scale != "training1")
head(d)
```

@@

Populate a new df
```{r}
density <- d %>%
  group_by(degree, scale) %>%
  mutate(n = n()) %>%
  group_by(degree, scale, stars) %>%
  summarise(listener.p = n() / n[1])
```

Plot our pragmatic listener judgments
```{r}
write.csv(density, "models/e11.csv", row.names=FALSE)
```

```{r}
pdf("plots/e11.pdf", width = 8, height = 4)
qplot(stars, listener.p, facets = degree ~ scale, 
      geom="bar", stat = "identity",
      binwidth = 1, data=density)
dev.off()
```
